Algorithmic Approaches to Match Degraded Land Impressions

### 2017-09-11 degraded-paper.Rmd
Fix the references section

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

# Appendix

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, results='asis'}
all_combinations <- combn(unique(c(as.character(CCFs_features$Study), as.character(CCFs_features$Study))), 2, simplify = FALSE)

@@

```{r deghist, echo=FALSE, fig.cap='Histograms of matching probability, facetted by the degradation level and known match versus known non-match.', fig.height=9.5, fig.width=8}
p1 <- ggplot(data = filter(CCFs_withlands_plot, degrade_left == 0), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_right, scales = "free_y") +
    ggtitle("Left Fixed") +
    theme_bw()
p2 <- ggplot(data = filter(CCFs_withlands_plot, degrade_right == 0), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_left, scales = "free_y") +
    ggtitle("Right Fixed") +
    theme_bw()
p3 <- ggplot(data = filter(CCFs_withlands_plot, (degrade_left == 0 & degrade_right == 0) | (degrade_right != 0 & degrade_left != 0)), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_left+degrade_right, scales = "free_y") +
    ggtitle("Middle Fixed") +
    theme_bw()

@@

```{r firstscore, echo=FALSE, fig.cap='Score distributions for the naive approach to bullet matching, for known matches and known non-matches.'}
result <- CCFs_withlands %>%
    group_by(study.x, barrel.x, bullet.x, study.y, barrel.y, bullet.y) %>%
    summarise(forest = mean(head(sort(forest, decreasing = TRUE))), match = any(match))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
```

@@

```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, fig.pos='H', results='asis'}
all_combinations <- combn(unique(c(as.character(CCFs_features$Study), as.character(CCFs_features$Study))), 2, simplify = FALSE)

@@

```{r eval=FALSE, deghist, echo=FALSE, fig.cap='Histograms of matching probability, facetted by the degradation level and known match versus known non-match.', fig.height=9.5, fig.width=8, fig.pos='H'}
p1 <- ggplot(data = filter(CCFs_withlands_plot, degrade_left == 0), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_right, scales = "free_y") +
    ggtitle("Left Fixed") +
    theme_bw()
p2 <- ggplot(data = filter(CCFs_withlands_plot, degrade_right == 0), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_left, scales = "free_y") +
    ggtitle("Right Fixed") +
    theme_bw()
p3 <- ggplot(data = filter(CCFs_withlands_plot, (degrade_left == 0 & degrade_right == 0) | (degrade_right != 0 & degrade_left != 0)), aes(x = forest)) +
    geom_histogram() +
    facet_grid(match~degrade_left+degrade_right, scales = "free_y") +
    ggtitle("Middle Fixed") +
    theme_bw()

@@

```{r eval=FALSE, firstscore, echo=FALSE, fig.cap='Score distributions for the naive approach to bullet matching, for known matches and known non-matches.', fig.pos='H'}
result <- CCFs_withlands %>%
    group_by(study.x, barrel.x, bullet.x, study.y, barrel.y, bullet.y) %>%
    summarise(forest = mean(head(sort(forest, decreasing = TRUE))), match = any(match))

@@

# References

### 2017-09-11 degraded-paper.tex
Fix the references section

\section{Appendix}\label{appendix}

\begin{table}[ht]
\centering
\begin{tabular}{llllrlr}
  \hline
set1 & set2 & feature & matchtest & matchd & nonmatchtest & nonmatchd \\ 
  \hline
H252\_H252 & H252\_H44 & ccf & $<$ 0.0001 & 0.2723 & 1e-04 & 0.0189 \\ 
  H252\_H252 & H252\_H44 & cms & $<$ 0.0001 & 0.1751 & $<$ 0.0001 & 0.0245 \\ 
  H252\_H252 & H252\_H44 & D & $<$ 0.0001 & 0.2567 & $<$ 0.0001 & 0.1049 \\ 
  H252\_H252 & H252\_H44 & matches & $<$ 0.0001 & 0.1933 & $<$ 0.0001 & 0.0327 \\ 
  H252\_H252 & H252\_H44 & mismatches & $<$ 0.0001 & 0.2015 & 0.3537 & 0.0079 \\ 
  H252\_H252 & H252\_H44 & overlap & 0.0492 & 0.0984 & $<$ 0.0001 & 0.0276 \\ 
  H252\_H252 & H252\_H44 & rough\_cor & $<$ 0.0001 & 0.2647 & $<$ 0.0001 & 0.0970 \\ 
  H252\_H252 & H252\_H44 & sum\_peaks & 8e-04 & 0.1426 & 0.0015 & 0.0162 \\ 
  H252\_H252 & H44\_H44 & ccf & $<$ 0.0001 & 0.2160 & $<$ 0.0001 & 0.0257 \\ 
  H252\_H252 & H44\_H44 & cms & $<$ 0.0001 & 0.2515 & $<$ 0.0001 & 0.0467 \\ 
  H252\_H252 & H44\_H44 & D & $<$ 0.0001 & 0.2342 & $<$ 0.0001 & 0.1946 \\ 
  H252\_H252 & H44\_H44 & matches & $<$ 0.0001 & 0.2770 & $<$ 0.0001 & 0.0713 \\ 
  H252\_H252 & H44\_H44 & mismatches & $<$ 0.0001 & 0.2505 & 0.0414 & 0.0138 \\ 
  H252\_H252 & H44\_H44 & overlap & 0.2432 & 0.0906 & $<$ 0.0001 & 0.0408 \\ 
  H252\_H252 & H44\_H44 & rough\_cor & $<$ 0.0001 & 0.2242 & $<$ 0.0001 & 0.1718 \\ 
  H252\_H252 & H44\_H44 & sum\_peaks & 1e-04 & 0.1926 & $<$ 0.0001 & 0.0289 \\ 
  H252\_H44 & H44\_H44 & ccf & 0.1149 & 0.0883 & $<$ 0.0001 & 0.0259 \\ 
  H252\_H44 & H44\_H44 & cms & 0.111 & 0.0888 & $<$ 0.0001 & 0.0262 \\ 
  H252\_H44 & H44\_H44 & D & 0.2923 & 0.0724 & $<$ 0.0001 & 0.0906 \\ 
  H252\_H44 & H44\_H44 & matches & 0.0603 & 0.0977 & $<$ 0.0001 & 0.0423 \\ 
  H252\_H44 & H44\_H44 & mismatches & 0.3301 & 0.0700 & 0.1633 & 0.0096 \\ 
  H252\_H44 & H44\_H44 & overlap & 0.8231 & 0.0465 & 1e-04 & 0.0190 \\ 
  H252\_H44 & H44\_H44 & rough\_cor & 0.2671 & 0.0741 & $<$ 0.0001 & 0.0769 \\ 
  H252\_H44 & H44\_H44 & sum\_peaks & 0.047 & 0.1011 & 0.006 & 0.0147 \\ 
   \hline
\end{tabular}
\caption{Results for the Kolmogrov-Smirnov distributional test.} 
\label{tab:kstests}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics{degraded-paper_files/figure-latex/deghist-1.pdf}
\caption{\label{fig:deghist}Histograms of matching probability, facetted by
the degradation level and known match versus known non-match.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{degraded-paper_files/figure-latex/firstscore-1.pdf}
\caption{\label{fig:firstscore}Score distributions for the naive approach to
bullet matching, for known matches and known non-matches.}
\end{figure}

>>>>

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
